### 2017-12-28 icde/revision/sec-alg.tex

Our batch algorithm \batensemble  combines the importance scores computed by the citation, venue and author components with Eq.~(\ref{eq-ensemble}). It takes as input academic graph data $D$ and an iteration threshold $\epsilon$ and returns the scholarly article ranking of $D$. It first constructs the citation and venue graphs $G^c(V^c,E^c)$ and $G^v(V^v,E^v)$. Then it computes the prestige and popularity of citation, venue and author components.
Finally, it combines the  prestige and popularity of the three components to produce the final ranking with Eq.~(\ref{eq-ensemble}).

%\stitle{Popularity computation}. It is easy to see that
For popularity computation, it is easy to see that
(a) the popularity of articles can be computed by scanning through all citations once and adding the freshness of citations to their corresponding articles, by Eq.~(\ref{eq-pop}), and (b) the popularity of venues in a specific year or authors is computed by averaging the popularity of the articles published in the venues or by the authors.
That is, the popularity computation can be done by scanning through all citations once.

%\stitle{Prestige computation}. As the prestige of authors is defined as the average prestige of their published articles,
For prestige computation, as the one of authors is defined as the average prestige of their published articles,
it suffices to scan through all author-article  relationships for computing the prestige of authors. The prestige of  articles and venues in a specific year is computed by TWPageRank on citation graphs and venue graphs, which is usually computed in an iterative manner~\cite{Brin98:PageRank} and is the most expensive computation. Hence, the key of the computation of our approach is a good solution for computing TWPageRank.

@@

The main result here is to speed up computing TWPageRank by exploiting the {\em temporal order} of scholarly article citations.

@@

The main idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
We next show Claim~\ref{thm-prestige} by introducing and analyzing such a block-wise computation method.

@@

\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $G$.
To process an \scc instead of the entire graph, the edges of the citation or venue graph $G(V, E)$ are partitioned into the sets $E_i$ and $E_a$ of edges inside and across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.  The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to treat $E_i$ and $E_a$ separately as follows.

\vspace{-1ex}
\begin{scriptsize}
\begin{equation}\label{eq-prscc}
%\begin{split}
PR(v) =  d \sum_{(u,v)\in E_i} M_{u,v} PR(u)
   + d \sum_{(u,v)\in E_a} M_{u,v} PR(u) +  \frac{1-d}{n}.
%\end{split}
\end{equation}
\end{scriptsize}
%
\noindent
It first computes the block-wise graph $G'$ by treating \sccs in $G$ as single nodes, and then derives a topological order $O$ of nodes in $G'$. It then processes each \scc in the topological order  $O$ with Eq.~(\ref{eq-prscc}). Finally, it returns the TWPageRank vector. When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum of TWPageRank score changes is less than $\epsilon\cdot\frac{|scc|}{|V|}$, where $|scc|$ is the number of nodes in the \scc. Note that there must exist a topological order $O$, as the block-wise graph is a directed acyclic graph~\cite{CormenLRS01}.

@@

\stitle{Analysis of the block-wise algorithm}. While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
%
The block-wise graph and its topological order can be done in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and updating TWPageRank scores takes $O(|V|+|E_a|+t|E_i|)$ time as the edges in $E_a$ are only scanned once.
From these, we have the following.

\begin{lemma}
\label{prop-venue-time-complexity}
Given a citation graph or venue graph $G(V, E)$, algorithm \twprscc runs in  $O(|V|+|E_a|+t|E_i|)$ time, where $t$ is  the maximum number of iterations among all \sccs.
\end{lemma}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of citation/venue graphs and Web graphs~\cite{LeskovecLDM09}}
\label{tab-batch}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
 &   &  & \multicolumn{1}{c|}{\bf Largest }   & \multicolumn{1}{c|}{\bf \scc }    \\
\raisebox{1ex}[0pt]{\bf Graphs}      & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Nodes}} & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Edges}} &
\multicolumn{1}{c|}{\bf $|\scc|$} &  \multicolumn{1}{c|}{\bf edge ratio}    \\
\hline \hline
\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5K &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline
web-G  & 875,713 & 5,105,039 & \multicolumn{1}{c|}{434,818} & \multicolumn{1}{c|}{66.98\%} \\  %\hline
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Observation.} It is well-known that article citations obey a natural {\em temporal order}, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time. That is, $|E_i|$ is essentially small for the citation graphs of scholarly articles.

To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs and illustrate in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\%. In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.

@@

\stitle{Time complexity analysis of the batch algorithm}.
%
By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|V^v|+|E^c_a|+|E^v_a|+t|E^c_i|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the total number of author-article relationships.
%
The key of algorithm \batensemble is to compute TWPageRank with algorithm \twprscc.
Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$ at an extra space cost for the block-wise graphs of $G^c$ and $G^v$ and their topological orders.

>>>>

Our batch algorithm \batensemble  combines the importance scores computed by the citation, venue and author components. It takes as input academic graph data $D$ and an iteration threshold $\epsilon$ for TWPageRank and returns the scholarly article ranking. It first constructs the citation graph $G^c(V^c,E^c)$ and venue graph $G^v(V^v,E^v)$. Then it computes the prestige and popularity of citation, venue and author components.
Finally, it combines the  prestige and popularity of the three components to produce the final ranking with Eq.~(\ref{eq-ensemble}).

%\stitle{Popularity computation}. It is easy to see that
For popularity computation, it is easy to see that
(a) the popularity of articles can be computed by scanning through all citations once and adding the freshness of citations to their corresponding articles by Eq.~(\ref{eq-pop}), and (b) the popularity of venues in a specific year or authors is computed by averaging the popularity of the articles published in the venues or by the authors.
That is, the popularity computation can be done by scanning through all citations once.

%\stitle{Prestige computation}. As the prestige of authors is defined as the average prestige of their published articles,
For prestige computation, (a) as the one of authors is defined as the average prestige of their published articles,
it suffices to scan through all author-article  relationships for computing the prestige of authors. (b) The prestige of  articles and venues in a specific year is computed by TWPageRank on citation graphs and venue graphs, which is usually computed in an iterative manner~\cite{Brin98:PageRank} and is the most expensive computation. Hence, the key of the computation of our approach is a good solution for computing TWPageRank.

@@

The main result of this section is to speed up computing TWPageRank on scholarly data.
%by exploiting the {\em temporal order} of scholarly article citations.

@@

The core idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
We next show Claim~\ref{thm-prestige} by introducing and analyzing such a block-wise computation method.

@@

\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G(V, E)$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $PR$ of $G$.
%To process an \scc instead of the entire graph, 
To update scores of nodes in an \scc at a time, the edges of $G$ are partitioned into: (a) the set $E_i$ of edges inside \sccs and (b) the set $E_a$ of edges across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.  The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to separate $E$ into $E_i$ and $E_a$  as follows.

\vspace{-1ex}
\begin{scriptsize}
\begin{equation}\label{eq-prscc}
%\begin{split}
PR(v) =  d \sum_{(u,v)\in E_i} M_{u,v} PR(u)
   + d \sum_{(u,v)\in E_a} M_{u,v} PR(u) +  \frac{1-d}{n}.
%\end{split}
\end{equation}
\end{scriptsize}
%
\noindent
It first computes the block-wise graph $G'$ by treating \sccs in $G$ as single nodes, and derives a topological order $O$ of nodes in $G'$. It then processes each \scc in the topological order  $O$ with Eq.~(\ref{eq-prscc}). Finally, it returns the TWPageRank vector. When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum changes of of TWPageRank scores is less than $\epsilon |scc|/|V|$, where $|scc|$ is the number of nodes in the \scc. Note that there must exist a topological order $O$, as the block-wise graph is a directed acyclic graph~\cite{CormenLRS01}.

@@

\vspace{-1ex}
\stitle{Analysis of algorithm \twprscc}. While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
%
Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
From these, we have the following.

\begin{lemma}
\label{prop-venue-time-complexity}
Given a citation or venue graph $G(V, E)$, algorithm \twprscc runs in  $O(|V|+|E_a|+t|E_i|)$ time, where $t$ is  the maximum number of iterations among all \sccs.
\end{lemma}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of citation/venue graphs and Web graphs~\cite{LeskovecLDM09}}
\label{tab-batch}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
 &   &  & \multicolumn{1}{c|}{\bf Largest }   & \multicolumn{1}{c|}{\bf \scc }    \\
\raisebox{1ex}[0pt]{\bf Graphs}      & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Nodes}} & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Edges}} &
\multicolumn{1}{c|}{\bf $|\scc|$} &  \multicolumn{1}{c|}{\bf edge ratio}    \\
\hline \hline
\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5K &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline
web-G  & 875,713 & 5,105,039 & \multicolumn{1}{c|}{434,818} & \multicolumn{1}{c|}{66.98\%} \\  %\hline
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Observation.} It is well-known that citations obey a natural {\em temporal order}, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time. That is, {\em $|E_i|$ is essentially small for the citation and venue graphs of scholarly data}.

To verify this observation, we also collect the statistics of citation/venue graphs and Web graphs illustrated in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the \scc edge ratios $|E_i|/|E|$ are greater than 59\%. In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc only needs to scan $4|E|$ edges on citation and venue graphs, but over $59|E|$ edges on Web graphs.

@@

\stitle{Time complexity analysis of the batch algorithm}.
%
By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|E^c_a|+t|E^c_i|+|V^v|+|E^v_a|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the number of author-article relationships.
%
The key of algorithm \batensemble is to compute TWPageRank with algorithm \twprscc.
Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$ at an extra space cost for the block-wise graphs of $G^c$ and $G^v$ and their topological orders.

### 2017-12-28 icde/revision/sec-incAlg.tex

Scholarly articles are dynamic and continuously growing, and it is impractical to recompute ranking from scratch once they get updated. In this section, we present an incremental algorithm for our ranking model \ensemblerank.

@@

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of scholarly articles.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a   (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as article citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.

\stitle{Incremental popularity computation}.
The popularity of venues and authors is computed along the same lines as their batch counterparts of algorithm \batensemble,
as almost all venues and authors are affected  by the definitions of the popularity of venues and authors.

As the popularity of articles is defined as the sum of the freshness of all their citations, it is convenient to maintain in a dynamic scenario. Consider an updated citation graph $G^{c,+}(V^c\cup\Delta V^c, E^c\cup\Delta E^c)$ of $G^c(V^c, E^c)$, and the updated popularity $Pop_{c}^+(v)$ can be computed as:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
%
\noindent where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
$T_0$ (resp. $T^+_0$) is the current time on $G^c$ (resp. $G^{c,+}$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that it takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time to update the popularity.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

@@

\stitle{Auxiliary data structure maintenance}.
Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained: (a) the block-wise graph and  a mapping that, given a node of graph $G$, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
%
Observe that these auxiliary data structures can be easily maintained as follows.

@@

%%% affected/unaffected division
\stitle{Analyses of affected and unaffected areas}.
The TWPageRank vector $PR$ of graph $G$ is mainly affected in two ways.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of affected/unaffected areas}
\label{tab-inc}
%\begin{small}
%\vspace{-.5ex}
\eat{
\begin{tabular}{|c|c|c|}
\hline
{\bf Graphs} & $|V_A|$\hspace{2ex}$|V_B|$\hspace{3ex}$|V_C|$ & $|E_A|$\hspace{2ex}$|E_{AB}|$\hspace{2ex}$|E_B|$\hspace{2ex}$|E_{CB}|$\hspace{2ex}$|E_C|$ \\
\hline \hline
% citation graphs
\aan & $46.9\%$\ $47.3\%$\ $5.8\%$ & \ $2.9\%$\ $25.9\%$\ $60.5\%$\ $10.4\%$ \hspace{1ex} $0.3\%$ \\
\aminer & $81.4\%$ \hspace{1ex} $10.7\%$ \hspace{1ex} $7.8\%$ & $18.0\%$ \hspace{1ex} $53.2\%$ \hspace{1ex} $25.1\%$ \hspace{1ex} \ $2.3\%$ \hspace{1ex} $1.4\%$ \\
\magdata & $69.5\%$ \hspace{1ex} $25.9\%$ \hspace{1ex} $4.5\%$ & \ $1.0\%$ \hspace{1ex} $27.4\%$ \hspace{1ex} $64.5\%$ \hspace{1ex} \ $7.0\%$ \hspace{1ex} $0.1\%$ \\ \hline
% venue graphs
\aan & \ $2.1\%$ \hspace{1ex} $92.0\%$ \hspace{1ex} $5.8\%$ & \ $1.0\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $88.8\%$ \hspace{1ex} $10.0\%$ \hspace{1ex} $0.2\%$ \\
\aminer & $45.8\%$ \hspace{1ex} $47.7\%$ \hspace{1ex} $6.4\%$ & \ $0.0\%$ \hspace{1ex} \ $3.2\%$ \hspace{1ex} $95.4\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $0.1\%$ \\
\magdata & $12.4\%$ \hspace{1ex} $84.6\%$ \hspace{1ex} $3.0\%$ & \ $0.0\%$ \hspace{1ex} \ $0.1\%$ \hspace{1ex} $92.6\%$ \hspace{1ex} \ $7.1\%$ \hspace{1ex} $0.1\%$ \\
 \hline
\end{tabular}
}
\begin{tabular}{|c|c c c|c c c|}
\hline
 & \multicolumn{3}{c|}{\bf Citation graphs on}   & \multicolumn{3}{c|}{\bf Venue graphs on}    \\
\raisebox{1ex}[0pt]{\bf Statis.} & \aan & \aminer & \magdata & \aan & \aminer & \magdata \\
\hline \hline
$|V_A|$ & 47.4\% & 52.3\% & 69.2\% & 2.1\% & 8.7\% & 12.4\% \\
$|V_B|$ & 46.8\% & 40.0\% & 26.3\% & 92.0\% & 84.8\% & 84.6\% \\
$|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
% venue graphs
$|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\
$|E_{AB}|$ & 26.5\% & 30.2\% & 26.6\% & \ 1.2\% & \ 0.2\% & \ 0.1\% \\
$|E_B|$ & 59.8\% & 59.3\% & 65.5\% & 88.6\% & 92.3\% & 92.6\% \\
$|E_{CB}|$ & 10.4\% & \ 7.2\% & \ 7.0\% & 10.0\% & \ 7.3\% & \ 7.1\% \\
$|E_C|$ & \ 0.3\% & \ 0.9\% & \ 0.1\% & \ 0.2\% & \ 0.2\% & \ 0.1\% \\ \hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

>>>>

Scholarly data is dynamic and continuously growing, and it is impractical to recompute ranking from scratch once it gets updated. In this section, we present an incremental algorithm for our ranking model \ensemblerank.

@@

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.

\stitle{Incremental popularity computation}.
As the popularity of articles is defined as the sum of the freshness of their citations, it is convenient to maintain dynamically. Consider an updated citation graph $G^{c,+}(V^c\cup\Delta V^c, E^c\cup\Delta E^c)$ of $G^c(V^c, E^c)$, and the updated popularity $Pop_{c}^+(v)$ can be computed as:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
%
\noindent where $Pop^+_c(v)$ (resp. $Pop_c(v)$) is the popularity of node $v$ on $G^{c,+}$ (resp. $G^c$), and
$T^+_0$ (resp. $T_0$) is the current time on $G^{c,+}$ (resp. $G^c$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

The popularity of venues and authors is computed along the same lines as their batch counterparts of algorithm \batensemble,
as almost all venues and authors are affected  by the definitions of the popularity of venues and authors.

@@

\stitle{Auxiliary data structure maintenance}.
Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained: (a) the block-wise graph and  a mapping that, given a node of the citation or venue graph, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
%
Observe that these auxiliary data structures can be easily maintained as follows.

@@

%%% affected/unaffected division
\vspace{-1ex}
\stitle{Analysis of affected and unaffected areas}.
The TWPageRank vector $PR$ of graph $G$ is mainly affected in two ways.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of affected/unaffected areas}
\label{tab-inc}
%\begin{small}
\vspace{-.5ex}
\eat{
\begin{tabular}{|c|c|c|}
\hline
{\bf Graphs} & $|V_A|$\hspace{2ex}$|V_B|$\hspace{3ex}$|V_C|$ & $|E_A|$\hspace{2ex}$|E_{AB}|$\hspace{2ex}$|E_B|$\hspace{2ex}$|E_{CB}|$\hspace{2ex}$|E_C|$ \\
\hline \hline
% citation graphs
\aan & $46.9\%$\ $47.3\%$\ $5.8\%$ & \ $2.9\%$\ $25.9\%$\ $60.5\%$\ $10.4\%$ \hspace{1ex} $0.3\%$ \\
\aminer & $81.4\%$ \hspace{1ex} $10.7\%$ \hspace{1ex} $7.8\%$ & $18.0\%$ \hspace{1ex} $53.2\%$ \hspace{1ex} $25.1\%$ \hspace{1ex} \ $2.3\%$ \hspace{1ex} $1.4\%$ \\
\magdata & $69.5\%$ \hspace{1ex} $25.9\%$ \hspace{1ex} $4.5\%$ & \ $1.0\%$ \hspace{1ex} $27.4\%$ \hspace{1ex} $64.5\%$ \hspace{1ex} \ $7.0\%$ \hspace{1ex} $0.1\%$ \\ \hline
% venue graphs
\aan & \ $2.1\%$ \hspace{1ex} $92.0\%$ \hspace{1ex} $5.8\%$ & \ $1.0\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $88.8\%$ \hspace{1ex} $10.0\%$ \hspace{1ex} $0.2\%$ \\
\aminer & $45.8\%$ \hspace{1ex} $47.7\%$ \hspace{1ex} $6.4\%$ & \ $0.0\%$ \hspace{1ex} \ $3.2\%$ \hspace{1ex} $95.4\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $0.1\%$ \\
\magdata & $12.4\%$ \hspace{1ex} $84.6\%$ \hspace{1ex} $3.0\%$ & \ $0.0\%$ \hspace{1ex} \ $0.1\%$ \hspace{1ex} $92.6\%$ \hspace{1ex} \ $7.1\%$ \hspace{1ex} $0.1\%$ \\
 \hline
\end{tabular}
}
\begin{tabular}{|c|c c c|c c c|}
\hline
 & \multicolumn{3}{c|}{\bf Citation graphs on}   & \multicolumn{3}{c|}{\bf Venue graphs on}    \\
\raisebox{1ex}[0pt]{\bf Statis.} & \aan & \aminer & \magdata & \aan & \aminer & \magdata \\
\hline \hline
$|V_A|$ & 47.4\% & 52.3\% & 69.2\% & 2.1\% & 8.7\% & 12.4\% \\
$|V_B|$ & 46.8\% & 40.0\% & 26.3\% & 92.0\% & 84.8\% & 84.6\% \\
$|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
% venue graphs
$|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\
$|E_{AB}|$ & 26.5\% & 30.2\% & 26.6\% & \ 1.2\% & \ 0.2\% & \ 0.1\% \\
$|E_B|$ & 59.8\% & 59.3\% & 65.5\% & 88.6\% & 92.3\% & 92.6\% \\
$|E_{CB}|$ & 10.4\% & \ 7.2\% & \ 7.0\% & 10.0\% & \ 7.3\% & \ 7.1\% \\
$|E_C|$ & \ 0.3\% & \ 0.9\% & \ 0.1\% & \ 0.2\% & \ 0.2\% & \ 0.1\% \\ \hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

### 2017-12-28 icde/revision/sec-model.tex

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
\markedb{To do this, an {\em author citation graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB). It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

>>>>

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
\markedb{To do this, an {\em author graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. It is not hard to image that the number of edges in the author graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB). It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.
